---
title: "Ohlcv features"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{basic}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(finfeatures)
```

Data for predicting financial time series prices in general includes:

1. Market data
2. Fundamental data
3. Alternative data.

For now, we only implement features generation for market data.

# OhlcvFeatures

# OHLCV data

Practioners mostly use OHLCV data in their analysis. If you want to use OHLCV 
data in finfeatures package you should first create `Ohlcv` class:

``` {r}
data(spy_hour)
ohlcv = Ohlcv$new(spy_hour, date_col = "datetime")
```

# Rolling indicators

```{r}
# RollingExuberInit = RollingExuber$new(windows = c(200, 400),
#                                       workers = 4L,
#                                       at = 1:nrow(ohlcv$X),
#                                       lag = 1L,
#                                       na_pad = TRUE,
#                                       simplify = FALSE)
# exuber_features = RollingExuberInit$get_rolling_features(ohlcv)

```

```{r}
####### DEBUG ######
# library(ggplot2)
# 
# ggplot(exuber_features, aes(x = date)) +
#   geom_line(aes(y = exuber_200_0_bsadf))
# 
# 
# x <- Reduce(function(x, y) merge(x, y, by = c("symbol", "date"), all.x = TRUE, all.y = FALSE),
#             x = list(ohlcv$X, exuber_features))
# 
# ggplot(x, aes(x = date, y = close, colour = (exuber_200_0_bsadf > 1))) +
#   geom_line(aes(group = 1))
# 
# ggplot(x, aes(x = date)) +
#   geom_line(aes(y = close)) +
#   geom_point(aes(y = exuber_400_0_bsadf, color = "red", size = 2))

####### DEBUG ######  
```


Now we can calculate come common used features using `OhlcvFeatures` class:

``` {r}
RollingOhlcvFeatures = OhlcvFeatures$new(at = c(500, 600),
                                         windows = c(200, 300),
                                         quantile_divergence_window =  c(50, 100))
ohlcv_features = RollingOhlcvFeatures$get_ohlcv_features(ohlcv)
tail(ohlcv_features)
```




The simplest way to use the package is to use `Features` class, which creates all features:
